\documentclass{spelllist}

\usepackage{microtype}
\usepackage{booktabs}

\usepackage{lipsum}

\begin{document}
  \section*{Spell List}
  
  \subsection*{Orisons}
  \subsubsection*{Core}
  \begin{flushleft}
    \textbf{Bleed:} Causes a stabilized creature to resume dying.
    
    \textbf{Create Water:} Creates 2 gallons/level of pure water.
    
    \textbf{Detect Magic:} Detects spells and magic items within 60 ft.
    
    \textbf{Detect Poison:} Detects poison in one creature or object.
    
    \textbf{Guidance:} $+1$ on one attack roll, saving throw, or skill check.
    
    \textbf{Light:} Object shines like a torch.
    
    \textbf{Mending:} Makes minor repairs on an object.
    
    \textbf{Purify Food and Drink:} Purifies 1 cu ft/level of food or water.
    
    \textbf{Read Magic:} Read scrolls and spellbooks.
    
    \textbf{Resistance:} Subject gains $+1$ on saving throws.
    
    \textbf{Stabilize:} Cause a dying creature to stabilize.
    
    \textbf{Virtue:} Subject gains 1 temporary hp.
  \end{flushleft}
  
  \subsubsection*{Advanced Players Guide}
  \begin{flushleft}
    \textbf{Spark:} Ignites flammable objects.
  \end{flushleft}
  
  \subsection*{1st Level}
  \subsubsection*{Core}
  \begin{flushleft}
    \textbf{Bane:} Enemies take $-1$ on attack rolls and saves against fear.
    
    \textbf{Bless:} Allies gain $+1$ on attack rolls and saves against fear.
    
    \textbf{Bless Water\textsuperscript{M}:} Makes holy water.
    
    \textbf{Cause Fear:} One creature of 5 HD or less flees for 1d4 rounds.
    
    \textbf{Command:} One subject obeys selected command for 1 round.
    
    \textbf{Comprehend Languages:} You understand all spoken and written languages.
    
    \textbf{Cure Light Wounds:} Cures 1d8 damage $+1$/level (max $+5$).
    
    \textbf{Deathwatch:} Reveals how near death subjects within 30 ft are.
    
    \textbf{Detect Chaos/Evil/Good/Law:} Reveals creatures, spells or objects of selected alignment.
    
    \textbf{Detect Undead:} Reveals undead within 60 ft.
    
    \textbf{Divine Favor:} You gain $+1$ per three levels on attack and damage rolls.
    
    \textbf{Doom:} One subject takes $-2$ on attack rolls, damage rolls, saves and checks.
    
    \textbf{Endure Elements:} Exist comfortably in hot or cold regions.
    
    \textbf{Entropic Shield:} Ranged attacks against you have 20\% miss chance.
    
    \textbf{Hide from Undead:} Undead can't perceive one subject/level.
    
    \textbf{Inflict Light Wounds:} Touch deals 1d8 damage $+1$/level (max $+5$).
    
    \textbf{Magic Stone:} Three stones gain $+1$ on attack, deal 1d6$+1$ damage.
    
    \textbf{Magic Weapon:} Weapon gains $+1$ bonus.
    
    \textbf{Obsucring Mist:} Fog surrounds you.
    
    \textbf{Protection from Chaos/Evil/Good/Law:} $+2$ to AC and saves, plus additional protection against selected alignment.
    
    \textbf{Remove Fear:} Suppresses fear or gives $+4$ on saves against fear for one subject $+$ one per four levels.
    
    \textbf{Sanctuary:} Opponents can't attack you, and you can't attack.
    
    \textbf{Shield of Faith:} Aura grants $+2$ or higher deflection bonus.
    
    \textbf{Summon Moster I:} Summons extraplanar creature to fight for you.
  \end{flushleft}
  
  \subsubsection*{Advanced Players Guide}
  \begin{flushleft}
    \textbf{Ant Haul:} Triples carrying capacity of a creature.
    
    \textbf{Dancing Lantern:} Animates a lantern that follows you.
  \end{flushleft}
  
  \subsection*{2nd Level}
  \subsubsection*{Core}
  
  \begin{flushleft}
    \textbf{Aid:} $+1$ on attack rolls and saves against fear, 1d8 temporary hp $+1$/level (max $+10$)
    
    \textbf{Align Weapon:} Weapon becomes good, evil, lawful, or chaotic.
    
    \textbf{Augury MF:} Learns whether an action will be good or bad.
    \textbf{Bear’s Endurance:} Subject gains +4 to Con for 1 min./level.
    \textbf{Bull’s Strength:} Subject gains +4 to Str for 1 min./level.
    \textbf{Calm Emotions:} Calms creatures, negating emotion effects.
    \textbf{Consecrate\textsuperscript{M}:} Fills area with positive energy, weakening undead.
    \textbf{Cure Moderate Wounds:} Cures 2d8 damage + 1/level (max +10).
    \textbf{Darkness:} 20-ft. radius of supernatural shadow.
    \textbf{Death Knell:} Kills dying creature; you gain 1d8 temporary
    hp, +2 to Str, and +1 caster level.
    \textbf{Delay Poison:} Stops poison from harming target for 1 hour/level.
    \textbf{Eagle’s Splendor:} Subject gains +4 to Cha for 1 min./level.
    \textbf{Enthrall:} Captivates all within 100 ft. + 10 ft./level.
    \textbf{Find Traps:} Notice traps as a rogue does.
    \textbf{Gentle Repose:} Preserves one corpse.
    \textbf{Hold Person:} Paralyzes one humanoid for 1 round/level.
    \textbf{Inflict Moderate Wounds:} Touch attack, 2d8 damage + 1/level
    (max +10).
    \textbf{Make Whole:} Repairs an object.
    \textbf{Owl’s Wisdom:} Subject gains +4 to Wis for 1 min./level.
    \textbf{Remove Paralysis:} Frees creatures from paralysis or slow effect.
    \textbf{Resist Energy:} Ignores 10 (or more) points of damage/attack
    from specified energy type.
    \textbf{Restoration, Lesser:} Dispels magical ability penalty or
    repairs 1d4 ability damage.
    \textbf{Shatter:} Sonic vibration damages objects or crystalline
    creatures.
    \textbf{Shield Other\textsuperscript{F}:} You take half of subject’s damage.
    \textbf{Silence:} Negates sound in 20-ft. radius.
    \textbf{Sound Burst:} Deals 1d8 sonic damage to subjects; may stun them.
    \textbf{Spiritual Weapon:} Magic weapon attacks on its own.
    \textbf{Status:} Monitors condition, position of allies.
    \textbf{Summon Monster II:} Summons extraplanar creature to
    fight for you.
    \textbf{Undetectable Alignment:} Conceals alignment for 24 hours.
    \textbf{Zone of Truth:} Subjects within range cannot lie.
    
  \end{flushleft}
  
  \subsubsection*{Advanced Players Guide}
  
  \section*{Domains}
  \subsection*{Luck}
  \textbf{Granted Powers:} You are infused with luck, and your
mere presence can spread good fortune.

  \emph{Bit of Luck (Sp):} You can touch a willing creature as a
  standard action, giving it a bit of luck. For the next round,
  any time the target rolls a d20, he may roll twice and take
  the more favorable result. You can use this ability a number
  of times per day equal to $3 +$ your Wisdom modifier.
  
  \emph{Good Fortune (Ex):} At 6th level, as an immediate action,
  you can reroll any one d20 roll you have just made before
  the results of the roll are revealed. You must take the result
  of the reroll, even if it’s worse than the original roll. You can
  use this ability once per day at 6th level, and one additional
  time per day for every six cleric levels beyond 6th.
  
  \textbf{Domain Spells:} 1st-true strike, 2nd-aid, 3rd-
  protection from energy, 4th-freedom of movement, 5th-break
  enchantment, 6th-mislead, 7th-spell turning, 8th-moment
  of prescience, 9th-miracle.
  
  \subsection*{Travel}
  \textbf{Granted Powers:} You are an explorer and find
  enlightenment in the simple joy of travel, be it by foot or
  conveyance or magic. Increase your base speed by 10 feet.
  
  \emph{Agile Feet (Su):} As a free action, you can gain increased
  mobility for 1 round. For the next round, you ignore all
  difficult terrain and do not take any penalties for moving
  through it. You can use this ability a number of times per
  day equal to 3 + your Wisdom modifier.
  
  \emph{Dimensional Hop (Sp):} At 8th level, you can teleport up
  to 10 feet per cleric level per day as a move action. This
  teleportation must be used in 5-foot increments and such
  movement does not provoke attacks of opportunity. You
  must have line of sight to your destination to use this
  ability. You can bring other willing creatures with you,
  but you must expend an equal amount of distance for each
  creature brought.
  
  \textbf{Domain Spells:} 1st-longstrider, 2nd-locate object, 3rd-
  fly, 4th-dimension door, 5th-teleport, 6th-find the path,
  7th-greater teleport, 8th-phase door, 9th-astral projection.
  
  \section*{Orisons}
  \begin{spell}
    \spellname{example}
    \luck
    \cleric
    \travel
    \castingtime{\oneround}
    \castingrange{5 miles}
    \spellschool{enchantment}
    \spelltarget{touch}
    \spellduration{5 years}
    \verbal
    \somatic
    \material{two goats}
    \divinefocus
    \focus{old sock}
    \savingthrow{will}
    \spelldescription{this is the description of the spell}
  \end{spell}
  
  \begin{spell}
    \spellname{Bleed}
    \spellschool{Necromancy}
    \cleric
    \castingtime{\oneaction}
    \verbal\somatic
    \castingrange{\shortrange}
    \spelltarget{One living creature}
    \spellduration{Instantaneous}
    \savingthrow{Will netages; Spell Resist: yes}
    \spelldescription{You cause a living creature that is below 0 hit points but stabilized to resume dying. Upon casting this spell, you target a living creature that has -1 or fewer hit points. That creature begins dying, taking 1 point of damage per round. The creature can be stabilized later normally. This spell causes a creature that is dying to take 1 point of damage.}
  \end{spell}
  
  \begin{spell}
    \spellname{Create Water}
    \spellschool{Conjuration (creation) [water]}
    \cleric
    \castingtime{\oneaction}
    \verbal\somatic
    \castingrange{\shortrange}
    \spelleffect{Up to 2 gallons of water/level}
    \spellduration{Instantaneous}
    \savingthrow{none; Spell Resist: no}
    \spelldescription{This spell generates wholesome, drinkable water, just like clean rain water. Water can be created in an area as small as will actually contain the liquid, or in an area three times as lange---possibly creating a downpour or filling many small receptacles. This water disappears after 1 day if not consumed. 
    
    Note: Conjuration spells can't create substances or objects within a creature. Water weighs about 8 pounds per gallon. One cubic foot of water contains roughly 8 gallons and weighs about 60 pounds.}
  \end{spell}
  
  \begin{spell}
    \spellname{Detect Magic}
    \spellschool{Divination}
    \cleric
    \castingtime{\oneaction}
    \verbal\somatic
    \castingrange{60 ft.}
    \spellarea{Cone-shaped emanation}
    \spellduration{Concentration, up to 1 min/level (D)}
    \savingthrow{none; Spell Resist: no}
    \spelldescription{You detect magical auras. The amount of information revealed depends on how long you study a particular area or subject. 
    
    1st Round: Presence or absence of magical auras.
    
    2nd Round: Number of different magical auras and the power of the most potent aura.
    
    3rd Round: The strength and location of each aura. If the item or creatures bearing the auras are in line of sight, you can make \mbox{Knowledge (arcana)} skill checks to determine the school of magic involved in each. (Make one check per aura: DC 15 + spell level, or 15 + 1/2 caster level for nonspell effect.) If the aura emanates from a magic item, you can attempt to identify its properties (see Spellcraft).
    
    Magical areas, multiple types of magic, or strong local magical emanations may distort or conceal weaker auras.
    
    Aura Strength: An aura's power depends on a spell's functioning spell level or an item's caster level; see the accompanying table. If an aura falls into more than one category, detect magic indicates the stronger of the two.
    
    Lingering Aura: A magical aura lingers after its original source dissipates (in the case of a spell) or is destroyed (in the case of a migac item). If detect magic is cast and directed at such a location the spell indicates an aura strength of dim (even weaker than a faint aura). How long the aura lingers at this dim level depends on its original power:
    
    \begin{center}
      \begin{tabular}{ll}
        \toprule
        Original Strength   & Duration of Lingering Aura\\
        \midrule
        Faint           & 1d6 rounds\\
        Moderate        & 1d6 minutes\\
        Strong          & 1d6$\times$10 minutes\\
        Overwhelming    & 1d6 days\\
        \bottomrule
      \end{tabular}
    \end{center}
    
    Outsiders and elementals are not magical in themselves, but if the are summoned, the conjuration spell registers. Each round, you can turn to detect magic in a new area. The spell can penetrate barriers, but 1 foot of stone, 1 inch of common metal, a thin sheet of lead, or 3 feet of wood or dirt blocks it.
    
    Detect magic can be made permanent with a permanency spell.
  }
  \end{spell}
  
  \begin{spell}
    \spellname{Detect Poison}
    \spellschool{Divination}
    \cleric
    \castingtime{\oneaction}
    \verbal\somatic
    \castingrange{\shortrange}
    \spelltarget{One creature, one object, or a 5~ft. cube}
    \spellduration{Instantaneous}
    \savingthrow{none; Spell Resist: no}
    \spelldescription{You determine whether a creature, object, or area has been poisoned or is poisonous. You can determine the exact type of poison with a DC 20 wisdom check. A character with the \mbox{Craft (alchemy)} skill may try a DC 20 \mbox{Craft (alchemy)} check prior to the wisdom check. The spell can penetrate barriers, but 1 foot of stone, 1 inch of common metal, a thin sheet of lead, or 3 feet of wood or dirt blocks it.}
  \end{spell}
  
  \begin{spell}
    \spellname{Guidance}
    \spellschool{Divination}
    \cleric
    \castingtime{\oneaction}
    \verbal\somatic
    \castingrange{Touch}
    \spelltarget{Creature touched}
    \spellduration{1 minute or until discharged}
    \savingthrow{Will negates (harmless)}
    \resistno
    \spelldescription{This spell imbues the subject with a touch of divine guidance. The creature gets a +1 competence bonus on a single attack roll, saving throw, or skill check. It must choose to use the bonus before making the roll to which it applies.}
  \end{spell}
  
  \begin{spell}
    \spellname{Light}
    \spellschool{Evocation}
    \cleric
    \castingtime{\oneaction}
    \verbal\divinefocus
    \castingrange{Touch}
    \spelltarget{Object touched}
    \spellduration{10 min/level}
    \savingthrow{none}
    \resistno
    \spelldescription{This spell causes a touched object to glow like a torch, shedding normal light in a 20~foot radius from the point touched, and increasing the light level for an additional 20~feet by one step, up to normal light (darkness becomes dim light, and dim light becomes normal light). In an area of normal or bright light, this spell has no effect. The effect is immobile, but it can be cast on a movable object.
    
    You can only have one light spell active at any one time. If you cast this spell while another casting is still in effect, the previous casting is dispelled. If you make this spell permanent (through permanency or a similar effect), it does not count against this limit. Light can be used to counter or dispel any darkness spell of equal or lower spell level.}
  \end{spell}
  
  \begin{spell}
    \spellname{Mending}
    \spellschool{Transmutation}
    \cleric
    \castingtime{10 minutes}
    \verbal\somatic
    \castingrange{10~ft.}
    \spelltarget{One object of up to 1 lb/level}
    \spellduration{Instantaneous}
    \savingthrow{Will negates (harmless, object)}
    \resistyes
    \spelldescription{This spell repairs damaged objects, restoring 1d4 hit points to the object. If the object has the broken condition, this condition is removed if the object is restored to at least half its original hit point.s All of the pieces of an object must be present for this spell to function. Magic items can be repaired by this spell, but you must have a caster level equal to or higher than that of the object. Magic items that are destroyed (at 0 hit points or less) can be repaired with this spell, but this spell does not restore their magic abilities. This spell does not affect creatures (including constructs). This spell has no effect on objects that have been warped or otherwise transmuted, but it can still repair damage done to such items.}
  \end{spell}
  
  \begin{spell}
    \spellname{Purify Food and Drink}
    \cleric
    \spellschool{Transmutation}
    \castingtime{\oneaction}
    \verbal\somatic
    \castingrange{10~ft}
    \spelltarget{1 cu ft/level of contaminated food and water}
    \spellduration{Instantaneous}
    \savingthrow{Will negates (object)}
    \resistyes
    \spelldescription{This spell makes spoiled, rotten, diseased, poisonous, or otherwise contaminated food and water pure and suitable for eating and drinking. This spell does not prevent subsequent natural decay or spoilage. Unholy water and similar food and drink of significance is spoiled by purify food and drink, but the spell has no effect on creatures of any type nor upon magic potions. Water weighs about 8 pounds per gallon. One cubit foot of water contains roughly 8 gallons and weighs about 60 pounds.}
  \end{spell}
  
  \begin{spell}
    \spellname{Read Magic}
    \spellschool{Divination}
    \cleric
    \castingtime{\oneaction}
    \verbal\somatic\focus{A clear crystal or mineral prism}
    \castingrange{Personal}
    \spelltarget{You}
    \spellduration{You can decipher magical inscriptions on objects---books, scrolls, weapons, and the like---that would otherwise be unintelligible. This deciphering does not normally invoke the magic contained in the writing, although it may do so in the case of a cursed or trapped scroll. Furthermore, once the spell is cast and you have read the magical inscription, you are thereafter able to read that particular writing without recourse to the use of read magic. You can read at the rate of one page (250 words) per minute. The spell allows you to identify a glyph of warding with a DC~13 Spellcraft check, a greater glyph of warding with a DC~16 Spellcraft check, or any symbol spell with a Spellcraft check \mbox{(DC 10 + spell level)}.
    
    Read magic can be made permanent with a permanency spell.}
  \end{spell}
  
  \begin{spell}
    \spellname{Resistance}
    \spellschool{Abjuration}
    \cleric
    \castingtime{\oneaction}
    \verbal\somatic\divinefocus
    \castingrange{Touch}
    \spelltarget{Creature touched}
    \spellduration{1 minute}
    \savingthrow{Will negates (harmless)}
    \resistyes
    \spelldescription{You imbue the subject with magical energy that protects it from harm, granting it a +1 resistance bonus on saves.
    
    Resistance can be made permanent with a permanency spell.}
  \end{spell}
  
  \begin{spell}
    \spellname{Stabilize}
    \spellschool{Conjuration (healing)}
    \cleric
    \castingtime{\oneaction}
    \verbal\somatic
    \castingrange{\shortrange}
    \spelltarget{One living creature}
    \spellduration{Instantaneous}
    \savingthrow{Will negates (harmless)}
    \resistyes
    \spelldescription{Upon casting this spell, you target a living creature that has $-1$ or fewer hit points. That creature is automatically stabilized and does not lose any further hit points. If the creature later takes damage, it continues dying normally.}
  \end{spell}
  
  \begin{spell}
    \spellname{Virtue}
    \spellschool{Transmutation}
    \cleric
    \castingtime{\oneaction}
    \verbal\somatic\divinefocus
    \castingrange{Touch}
    \spelltarget{Creature touched}
    \spellduration{1 minute}
    \savingthrow{None}
    \resistyes
    \spelldescription{With a touch, you infuse a creature with a tiny surge of life, granting the subject 1 temporary hit point.}
  \end{spell}
  
  \section*{1st Level}
  
  \begin{spell}
    \spellname{Bane}
    \spellschool{Enchantment (compulsion) [fear, mind-affecting]}
    \cleric
    \castingtime{\oneaction}
    \verbal\somatic\divinefocus
    \castingrange{50~ft}
    \spellarea{50~ft radius burst, centered on you}
    \spellduration{1 min/level}
    \savingthrow{Will negates}
    \resistyes
    \spelldescription{Bane fills your enemies with fear and doubt. Each affected creature takes a $-1$ penalty on attack rolls and a $-1$ penalty on saving throws against fear effects. Bane counters and dispels bless.}
  \end{spell}
  
  \begin{spell}
    \spellname{Bless}
    \spellschool{Enchantment (compulsion) [mind-affecting]}
    \cleric
    \castingtime\oneaction
    \verbal\somatic\divinefocus
    \castingrange{50 ft}
    \spellarea{The caster and all allies within a 50~ft burst, centered on the caster}
    \spellduration{1 min/level}
    \savingthrow{None}
    \resistyes
    \spelldescription{Bless fills your allies with courage. Each ally gains a $+1$ morale bonus on attack rolls and on saving throws against fear effects.
    
    Bless counters and dispels bane.}
  \end{spell}
  
  \begin{spell}
    \spellname{Bless Water}
    \spellschool{Transmutation [good]}
    \cleric
    \verbal\somatic\material{5 pounds of powdered silver worth 25 gp}
    \castingrange{Touch}
    \spelltarget{Flask of water touched}
    \spellduration{Instantaneous}
    \savingthrow{Will negates (object)}
    \resistyes
    \spelldescription{This transmutation imbues a flask (1~pint) of water with positive energy, turning it into holy water (see page 160).}
  \end{spell}
  
  \begin{spell}
    \spellname{Cause Fear}
    \spellschool{necromancy [fear, mind-affecting]}
    \cleric
    \castingtime{\oneaction}
    \verbal\somatic
    \castingrange{\shortrange}
    \spelltarget{One living creature with 5 or fewer HD}
    \spellduration{1d4 rounds or 1 round; see text}
    \savingthrow{Will partial}
    \resistyes
    \spelldescription{The affected creature becomes frightened. If the subject succeeds on a Will save, it is shaken for 1 round. Creatures with 6 or more HD are immune to this effect. Cause fear counters and dispels remove fear.}
  \end{spell}
  
  \begin{spell}
    \spellname{Command}
    \spellschool{Enchantment (compulsion) [language-dependent, mind-affecting]}
    \cleric
    \verbal
    \castingrange{\shortrange}
    \spelltarget{One living creature}
    \spellduration{\oneround}
    \savingthrow{Will negates}
    \resistyes
    \spelldescription{You give the subject a single command, which it obeys to the best of its ability at its earliest opportunity. You may select from the following options.
    
    \emph{Approach:} On its turn, the subject moves toward you as quickly and directly as possible for 1 round. The creature may do nothing but move during its turn, and it provokes attacks of opportunity for this movement as normal.
    
    \emph{Drop:} On its turn, the subject drops whatever it is holing. It can't pick up any dropped item until its next turn.
    
    \emph{Fall:} On its turn, the subject falls to the ground and remains prone for 1 round. It may act normally while prone but takes any appropriate penalties.
    
    \emph{Flee:} On its turn, the subject moves away from you as quickly as possible for 1 round. It may do nothing but move during its turn, and itprovokes attacks of opportunity for this movement as normal.
    
    \emph{Halt:} The subject stands in place for 1 round. It may not take any actions but is not considered helpless.
    
    If the subject can't carry out your command on its next turn, the spell automatically fails.}
  \end{spell}
  
  \begin{spell}
    \spellname{Comprehend Languages}
    \cleric\luck
    \spellschool{Divination}
    \castingtime{\oneaction}
    \verbal\somatic\divinefocus
    \castingrange{Personal}
    \spelltarget{You}
    \spellduration{10 min/level}
    \spelldescription{You can understand the spoken words of creatures or read otherwise incomprehensible written messages. The ability ot read does not necessarily impart insight into the material, merely its literal meaning. The spell enables you to understand or read an unknown language, not speak or write it.
    
    Written material can be read at the rate of one page (250 words) per minute. Magical writing cannot be read, through the spell reveals that it is magical. This spell can be foiled by certain warding magic (such as secret page and illusory script spells). It does not decipher codes or reveal messages concealed in otherwise normal text.
    
    Comprehend languages can be made permanent with a permanency spell.}
  \end{spell}
  
  \begin{spell}
    \spellname{Cure Light Wounds}
    \spellschool{Conjuration (healing)}
    \cleric
    \castingtime{\oneaction}
    \verbal\somatic
    \castingrange{Touch}
    \spelltarget{Creature touched}
    \spellduration{Instantaneous}
    \savingthrow{Will half (harmless)}
    \resistyes
    \spelldescription{When laying your hand upon a living creature, you channel positive energy that cures 1d8 points of damage $+1$ point per caster level (maximum $+5$). Since undead are powered by negative energy, this spell deals damage to them instead of curing their wounds. An undead creature can apply spell resistance, and can attempt a Will save to take half damage.}
  \end{spell}
  
  \begin{spell}
    \spellname{Deathwatch}
    \spellschool{Necromancy}
    \cleric
    \castingtime\oneaction
    \verbal\somatic
    \castingrange{30 ft}
    \spellarea{Cone-shaped emanation}
    \spellduration{10 min/level}
    \savingthrow{none}
    \resistno
    \spelldescription{Using the powers of necromancy, you can determine the condition of creatures near death within the spell's range. You instantly know whether each creature within the area is dead, fragile (alive and wounded, with 3 or fewer hit points left), fighting off death (alive with 4 or more hit points), healthy, undead, or neither alive nor dead (such as a construct). Deathwatch sees through any spell or ability that allows creatures to feign death.}
  \end{spell}
  
  \begin{spell}
    \spellname{Detect Chaos}
    \spellschool{Divination}
    \cleric
    \verbal\somatic\divinefocus
    \spelldescription{This spell functions like detect evil, except thath it detects the auras of chaotic creatures, clerics of chaotic deities, chaotic spells, and chaotic magic items, and you are vulnerable to an overwhelming chaotic aura if you are lawful.}
  \end{spell}
  
  \begin{spell}
    \spellname{Detect Evil}
    \spellschool{Divination}
    \cleric
    \castingtime\oneaction
    \verbal\somatic\divinefocus
    \castingrange{60 ft}
    \spellarea{Cone-shaped emanation}
    \spellduration{Concentration, up to 10 min/level (D)}
    \savingthrow{None}
    \resistno
    \spelldescription{You can sense the presence of evil. The amount of information revealed depends on how long you study a particular area or subject. 
    \emph{1st Round:} Presence or absence of evil.
    
    \emph{2nd Round:} Number of evil auras (creatures, objects, or spells) in the area and the power of the most potent evil aura present.
    
    If you are of good alignment, and the strongest evil aura's power is overwhelming (see below), and the HD or level of the aura's source is at least twice your character level, you are stunned for 1 round and the spell ends.
    
    \emph{3rd Round:} The power and location of each aura. If an aura is outside your line of sight, then you discern its direction but not its exact location.
    
    \emph{Aura Power:} An evil aura's power depends on the type of evil creature or object that you're detecting and its HD, caster level, or (in the case of a cleric) class level; see the table on the previous page. If an aura falls into more than one strength category, the spell indicates the stronger of the two. 
    
    \emph{Lingering Aura:} An evil aura lingers after its original source dissipates (in the case of a spell) or its destroyed (in the case of a creature or magic item). If detect evil is cast and directed at such a location, the spell indicates an aura strength of dim (even weaker than a faint aura). How long the aura lingers at this dim level depends on its original power:
    
    \begin{center}
      \begin{tabular}{ll}
        \toprule
        Original Strength   & Duration of Lingering Aura\\
        \midrule
        Faint       & 1d6 rounds\\
        Moderate    & 1d6 minutes\\
        Strong      & 1d6$\times$10 minutes\\
        Overwhelming  & 1d6 days\\
        \bottomrule
      \end{tabular}
    \end{center}
    
    Animals, traps, poisons, and other potential perils are not evil, and as such this spell does not detect them. Creatures with actively evil intents count as evil creatures for the purpose of this spell.
    
    Each round you can turn to detect evil in a new area. The spell can penetrate barriers, but 1 foot of stone, 1 inch of common metal, a thin sheat of lead, or 3 feet of wood or dirt blocks it.
  }
  \end{spell}
  
  \begin{spell}
    \spellname{Detect Good}
    \spellschool{Divination}
    \cleric
    \verbal\somatic\divinefocus
    \spelldescription{This spell functions like detect evil, except that it detects the auras of good creatures, clerics, or paladins of good deities, good spells, and good magic items, and you are vulnerable to an overwhelming good aura if you are evil.}
  \end{spell}
  
  \begin{spell}
    \spellname{Detect Law}
    \spellschool{Divinations}
    \cleric
    \verbal\somatic\divinefocus
    \spelldescription{This spell functions like detect evil, except that it detects the auras of lawful creatures, clerics of lawful deities, lawful spells, and lawful magic items, and you are vulnerable to an overwhelming lawful aura if you are chaotic.}
  \end{spell}
  
  \begin{spell}
    \spellname{Detect Undead}
    \spellschool{Divinations}
    \cleric
    \castingtime\oneaction
    \verbal\somatic\divinefocus
    \castingrange{60 ft}
    \spellarea{Cone-shaped emanation}
    \spellduration{Concentration, up to 1 minute/level}
    \savingthrow{None}
    \resistno
    \spelldescription{You can detect the aura that surrounds undead creatures. The amount of information revealed depends on how long you study a particular area.
    
    \emph{1st Round:} Presence or abesnce of undead auras.
    
    \emph{2nd Round:} Number of undead auras in the area and the strength of the strongest undead aura present. If you are of good alignment, and the strongest undead aura's strength is overwhelming (see below), and the creature has HD of at least twice your character level, you are stunned for 1 round and the spell ends.
    
    \emph{3rd Round:} The strength and location of each undead aura. If an aura is outside your line of sight, then you discern its direction but not its exact location.
    
    \emph{Aura Strength:} The strength of an undead aura is determined by the HD of the undead creature, as given on the table below. 
    
    \emph{Lingering Aura:} An undead aura lingers after its original source is destroyed. If detect undead is cast and directed at such a location, the spell indicates an aura strength of dim (even weaker than a faint aura). How long the aura lingers at this dim level depends on its original power, as given on the table below.
    
    \begin{center}
      \begin{tabular}{lll}
        \toprule
        HD      & Strength      & Aura Duration\\
        \midrule
        $\leq 1$    & Faint       & 1d6 rounds\\
        2--4        & Moderate    & 1d6 minutes\\
        5--10       & Strong      & 1d6$\times$10 minutes\\
        $\geq 11$   & Overwhelming  & 1d6 days\\
        \bottomrule
      \end{tabular}
    \end{center}
    
    Each round, you can turn to detect undead in a new area. The spell can penetrate barriers, but 1 foot of stone, 1 inch of common metal, a thin sheet of lead, or 3 feet of wood or dirt blocks it.}
  \end{spell}
  
  \begin{spell}
    \spellname{Divine Favor}
    \spellschool{Evocation}
    \cleric
    \castingtime\oneaction
    \verbal\somatic\divinefocus
    \castingrange{Personal}
    \spelltarget{You}
    \spellduration{1 minute}
    \spelldescription{Calling upon the strength and wisdom of a deity, you gan a $+1$ luck bonus on attack and weapon damage rolls for every three caster levels you have (at least $+1$, maximum $+3$). The bonus doesn't apply to spell damage.}
  \end{spell}
  
  \begin{spell}
    \spellname{Doom}
    \spellschool{Necromancy [fear, mind-affecting]}
    \cleric
    \castingtime\oneaction
    \verbal\somatic\divinefocus
    \castingrange\mediumrange
    \spelltarget{One living creature}
    \spellduration{1 min/level}
    \savingthrow{Will negates}
    \resistyes
    \spelldescription{This spell fills a single subject with a feeling of horrible dread that causes it to become shaken.}
  \end{spell}
  
  \begin{spell}
    \spellname{Endure Elements}
    \cleric
  \end{spell}
  
  \begin{spell}
    \spellname{Entropic Shield}
    \cleric
  \end{spell}
  
  \begin{spell}
    \spellname{Hide from Undead}
    \cleric
  \end{spell}
  
  \begin{spell}
    \spellname{Inflict Light Wounds}
    \cleric
  \end{spell}
  
  \begin{spell}
    \spellname{Magic Stone}
    \cleric
  \end{spell}
  
  \begin{spell}
    \spellname{Obscuring Mist}
    \cleric
  \end{spell}
  
  \begin{spell}
    \spellname{Protection from Chaos/Evil/Good/Law}
    \cleric
  \end{spell}
  
  \begin{spell}
    \spellname{Remove Fear}
    \cleric
  \end{spell}
  
  \begin{spell}
    \spellname{Sanctuary}
    \cleric
  \end{spell}
  
  \begin{spell}
    \spellname{Shield of Faith}
    \cleric
  \end{spell}
  
  \begin{spell}
    \spellname{Summon Monster I}
    \cleric
  \end{spell}
  
  \section*{2nd Level}
  
  \begin{spell}
    \spellname{Aid}
    \cleric
  \end{spell}
  
  \begin{spell}
    \spellname{Alight Weapon}
    \cleric
  \end{spell}
  
  \begin{spell}
    \spellname{Augury}
    \cleric
  \end{spell}
  
  \begin{spell}
    \spellname{Bear's Endurance}
    \cleric
  \end{spell}
  
  \begin{spell}
    \spellname{}
  \end{spell}
  
  \begin{spell}
    \spellname{Calm Emotions}
  \end{spell}
  
  \begin{spell}
    \spellname{Consecrate}
  \end{spell}
  
  \begin{spell}
    \spellname{Cure Moderate Wounds}
  \end{spell}
  
  \begin{spell}
    \spellname{Darkness}
  \end{spell}
  
  \begin{spell}
    \spellname{Death Knell}
  \end{spell}
  
  \begin{spell}
    \spellname{Delay Poison}
  \end{spell}
  
  \begin{spell}
    \spellname{Desecrate}
  \end{spell}
  
  \begin{spell}
    \spellname{Eagle's Splendor}
  \end{spell}
  
  \begin{spell}
    \spellname{Enthrall}
  \end{spell}
  
  \begin{spell}
    \spellname{Find Traps}
  \end{spell}
  
  \begin{spell}
    \spellname{Gentle Repose}
  \end{spell}
  
  \begin{spell}
    \spellname{Hold Person}
  \end{spell}
  
  \begin{spell}
    \spellname{Inflict Moderate Wounds}
  \end{spell}
  
  \begin{spell}
    \spellname{Make Whole}
  \end{spell}
  
  \begin{spell}
    \spellname{Owl's Wisdom}
  \end{spell}
  
  \begin{spell}
    \spellname{Remove Paralysis}
  \end{spell}
  
  \begin{spell}
    \spellname{Resist Energy}
  \end{spell}
  
  \begin{spell}
    \spellname{Restoration, Lesser}
  \end{spell}
  
  \begin{spell}
    \spellname{Shatter}
  \end{spell}
  
  \begin{spell}
    \spellname{Shield Other}
  \end{spell}
  
  \begin{spell}
    \spellname{Silence}
  \end{spell}
  
  \begin{spell}
    \spellname{Sound Burst}
  \end{spell}
  
  \begin{spell}
    \spellname{Spiritual Weapon}
  \end{spell}
  
  \begin{spell}
    \spellname{Status}
  \end{spell}
  
  \begin{spell}
    \spellname{Summon Monster II}
  \end{spell}
  
  \begin{spell}
    \spellname{Undetectable Alignment}
  \end{spell}
  
  \begin{spell}
    \spellname{Zone of Truth}
  \end{spell}
  
  \begin{spell}
    \spellname{}
  \end{spell}
  
  \begin{spell}
    \spellname{}
  \end{spell}
  
  \begin{spell}
    \spellname{}
  \end{spell}
  
  \begin{spell}
    \spellname{}
  \end{spell}
  
  \begin{spell}
    \spellname{}
  \end{spell}
  
\end{document}
